How to select predictive models for decision-making or causal inference?

### 2025-01-16 how_to_select_latex.tex
publication: add data availability section

Lists the following:
\begin{itemize}
    \item Project name: Caussim
    \item Project home page: \url{https://github.com/soda-inria/caussim}
    \item Operating system(s): Platform independent
    \item Programming language: Python
    \item License: BSD 3-Clause License
\end{itemize}

@@

\paragraph{Oracle Bayes predictor}\label{remark:bayes_oracle} If we
have access to the oracle Bayes predictor for the outcome ie.~$f(x,
    a)=\mu(x, a)$, then all risks are equivalent up to the residual variance:
\begin{equation}
    \tau\text{-risk}(\mu) = \mathbb E_{X\sim p(X)}[(\tau(X) - \tau_{\mu}(X))^2] = 0
\end{equation}
\begin{align}
    \mu\text{-risk}(\mu) & = \mathbb E_{(Y, X, A) \sim p(Y;X;A)}[\big( Y - \mu_A(X)\big)^2] \\
                         & = \int_{\mathcal X, \mathcal A}
    \,\varepsilon(x,a)^2 p(a \mid x) \,p(x) \,dx\,da  \leq \sigma_B^{2}(0) + \sigma_B^{2}(1) \nonumber
\end{align}
\begin{equation}
    \mu\text{-risk}_{IPW}(\mu) = \sigma_B^{2}(0) + \sigma_B^{2}(1)  \quad \text{from Lemma \ref{apd:proofs:mu_risk_ipw_link_mu}}
    %\notag
\end{equation}
\begin{multline}
    R\text{-risk}(\mu) = \tilde{\sigma}_B^{2}(0) + \tilde{\sigma}_B^{2}(1)
    \leq \sigma_B^{2}(0) + \sigma_B^{2}(1)  \\  \text{from Proposition \ref{theory:prop:r_risk_rewrite}}%\notag
\end{multline}

>>>>

\subsection{Source code to replicate the experiments of the paper}

The following repository is self-contained to allow anyone to replicate all experiments of the paper. It contains different codes to cover the full content of the paper. Thus it requires a bit of work to install and run the code.

\begin{itemize}
    \item Project name: Caussim
    \item Project home page: \url{https://github.com/soda-inria/caussim}
    \item Operating system(s): Platform independent
    \item Programming language: Python
    \item License: BSD 3-Clause License
\end{itemize}

\subsection{Standalone source code for the selection procedure}

Code for cross-validation to select the best predictive model to guide decision on potential intervention. The procedure implemented here is described in details in Algorithm \ref{problem:estimation_procedure:algo}. It serves as a simple plug-and-play code for a user that would want to use our procedure.

\begin{itemize}
    \item Project name: Causal Model Selection
    \item Project home page: \url{https://github.com/soda-inria/causal_model_selection}
    \item Operating system(s): Platform independent
    \item Programming language: Python
    \item License: BSD 2-Clause License
\end{itemize}

\section{Data availability}

\subsection{Semi-simulated datasets for the experiments}

The semi-simulated and simulated datasets used for the experiments are available at the following urls.

Detailed explanations on how to generate the datasets are available in the readme of the data section of our github: \url{https://github.com/soda-inria/caussim/tree/main/data}.

\begin{itemize}
    \item ACIC 2016: dataset provided through R package aciccomp2016: \url{https://github.com/vdorie/aciccomp}

    \item ACIC 2018: scaling subset from link to Synapse : \url{https://www.synapse.org/Synapse:syn11738767}

    \item TWINS: dataset from \url{https://github.com/AMLab-Amsterdam/CEVAE}, the version that we are using is on the following zenodo repository: \url{https://zenodo.org/records/14674618}.

    \item Caussim Dataset: generated dataset - instructions from \url{https://github.com/soda-inria/caussim}
\end{itemize}
\subsection{Experiments result data}

The result data generated by the experiments are available at a dedicated zenodo repository \url{https://zenodo.org/records/13765465}. We provide the data for the simulations and the semi-simulated datasets to allow an easy replication of the main graphic (Fig. \ref{fig:relative_kendalls_all_datasets}) in the result section (detailed steps on our github: \url{https://github.com/soda-inria/caussim/tree/main?tab=readme-ov-file#reports}).

@@

\paragraph{Oracle Bayes predictor}\label{remark:bayes_oracle} If we
have access to the oracle Bayes predictor for the outcome ie.~$f(x,
    a)=\mu(x, a)$, then all risks are equivalent up to the residual variance:
\begin{equation}
    \tau\text{-risk}(\mu) = \mathbb E_{X\sim p(X)}[(\tau(X) - \tau_{\mu}(X))^2] = 0
\end{equation}
\begin{align}
    \mu\text{-risk}(\mu) & = \mathbb E_{(Y, X, A) \sim p(Y;X;A)}[\big( Y - \mu_A(X)\big)^2] \\
                         & = \int_{\mathcal X, \mathcal A}
    \,\varepsilon(x,a)^2 p(a \mid x) \,p(x) \,dx\,da  \leq \sigma_B^{2}(0) + \sigma_B^{2}(1) \nonumber
\end{align}
\begin{equation}
    \mu\text{-risk}_{IPW}(\mu) = \sigma_B^{2}(0) + \sigma_B^{2}(1)
    %\notag
\end{equation}
\begin{multline}
    R\text{-risk}(\mu) = \tilde{\sigma}_B^{2}(0) + \tilde{\sigma}_B^{2}(1)
    \leq \sigma_B^{2}(0) + \sigma_B^{2}(1)  \\  \text{from Proposition \ref{theory:prop:r_risk_rewrite}}%\notag
\end{multline}
